Everest Bio

### 2021-10-25 slides/index.Rmd
Presentation for tool preparation complete from CICES

library(tidyverse)
# Link for the Figures
URL = c('https://raw.githubusercontent.com/fabbiocrux/Figures/main/')
```

@@

@@

@@

class: middle, left
background-image: url(`r paste0(URL, 'Climatelabs/Climatelabs.png')`)
background-position: center
background-size: contain

---
class: middle

# EU projects

.pull-left[
```{r , include=TRUE, echo=FALSE, fig.cap=" ", out.width = '60%', fig.align='center'}
knitr::include_graphics(paste0(URL, 'Smagrinet/Smagrinet-00.jpg'))
```
https://www.smagrinet.eu/

```{r , include=TRUE, echo=FALSE, fig.cap=" ", out.width = '60%', fig.align='center'}
knitr::include_graphics(paste0(URL, 'Digiterri/Digiterri'))
```

https://digiterri.eu/

```{r , include=TRUE, echo=FALSE, fig.cap=" ", out.width = '100%', fig.align='center'}
knitr::include_graphics(paste0(URL, 'Inedit/Inedit-00.png'))
```

https://www.inedit-project.eu/
]

@@

class: middle, center

Thanks !

>>>>

library(readxl)
library(here)
library(flextable)
library(tidyverse)

# Link for the Figures
URL = c('https://raw.githubusercontent.com/fabbiocrux/Figures/main/')

# CICES File
#file_cices <- list.files("../data/CICES")
CICES <- read_excel(here("../data/CICES/Finalised-V5.1_18032018.xlsx"), sheet = "CICES V5.1",  skip = 4 )
```

@@

---
# Tool for Everest Bio

.pull-left[
## Goal:
The main foal of the tool will be the identification of ES that are priorities for an industrial system inside a Territory.
]

---
## Structure of the tool

1. Identification of the Territory
1. Two types of actors:
   1. Industrial Agent: **Identification of LCI of the Process**
   1. Territorial Agent: **Identification of the Urban ES priorities**

@@

# CICES

1. .large.bg-yellow[Provisioning Services (biotic & Abiotic)]
1. .large.bg-yellow[Regulation & Maintenance (biotic & Abiotic)]
1. .large.bg-yellow[Cultural]

@@

# Provisioning Services (biotic & Abiotic)
## Plants

.pull-left[
**Territorial Question**

*Are cultivated plants (Terrestrial or Aquatic) strategic for the territory for nutrition, materials or energy ?*	
]

.pull-right[
**Industrial Question**

*Are cultivated plants (Terrestrial or Aquatic) impacted in certain level by the use of your technology or proposition ?*

```{r}
library(kableExtra)
# Version Flextable
# CICES_filter <- function(ID, size = 15, ...)
# {
#   Table <- CICES %>% select(Group, Class, Code) %>% 
#   filter(Code %in% ID) %>% 
#   flextable() %>% 
#   merge_v( j = "Group") %>% 
#   fontsize(size = size,  part = "all") %>% 
#   width(width = c(2,8,1))
#   return(Table)
# }

# Version Kableextrs
CICES_filter <- function(ID, size = 15, ...)
{
  Table <- 
    CICES %>% select(Group, Class, Code, 'Example Service') %>% 
    filter(Code %in% ID) %>% 
    kbl() %>%
    #kable_paper("striped", full_width = TRUE) %>% 
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = size)  %>% 
  collapse_rows(columns = 1:1)

  return(Table)
}

CICES_filter(ID=c("1.1.1.1", "1.1.1.2", "1.1.1.3", 
                     "1.1.2.1", "1.1.2.2", "1.1.2.3"), size = 15)

```

---
# Provisioning Services (biotic & Abiotic)
## Animals

.pull-left[
**Territorial Question**

*Are Reared animals (Terrestrial or Aquatic) strategic for the territory for nutrition, materials or energy ?*	
]

.pull-right[
**Industrial Question**

*Are Reared animals (Terrestrial or Aquatic) strategic for the territory for nutrition, materials or energy ?*
]

```{r}
CICES_filter(ID=c("1.1.3.1", "1.1.3.2", "1.1.3.3", "1.1.4.1", "1.1.4.2", "1.1.4.3"), size = 15)
```

@@

# Provisioning Services (biotic & Abiotic)
## Wild Animals & Plants

.pull-left[
**Territorial Question**

*Are Reared animals (Terrestrial or Aquatic) strategic for the territory for nutrition, materials or energy ?*	
]

.pull-right[
**Industrial Question**

*Are Reared animals (Terrestrial or Aquatic) strategic for the territory for nutrition, materials or energy ?*
]

```{r}
CICES_filter(ID=c("1.1.5.1","1.1.5.2","1.1.5.3","1.1.6.1","1.1.6.2","1.1.6.3"), size = 13)
```

---
# Provisioning Services (biotic & Abiotic)
## Genetic Material

.pull-left[
**Territorial Question**

*Is the Genetic material from plants, algae or fungi (including seed, spore or gamete production) an important element for the territory ?*	]

.pull-right[
**Industrial Question**

*Is the Genetic material from plants, algae or fungi (including seed, spore or gamete production) affected by the use of your technology int the territory ?*
]

```{r}
CICES_filter(ID=c("1.2.1.1","1.2.1.2","1.2.1.3","1.2.2.1","1.2.2.2","1.2.2.3"), size = 15)
```

# Provisioning Services (biotic & Abiotic)
## Water

.pull-left[
**Territorial Question**

*Is Water (for nutrition, materials or energy) an issue for the territory?*	]

.pull-right[
**Industrial Question**

*The is the impact of LCI?*
]

```{r ES_Provision_water}
CICES_filter(ID=c("4.2.1.1", "4.2.1.2", "4.2.1.3", "4.2.1.4", "4.2.2.1", "4.2.2.2", "4.2.2.3"
), size = 15)
```

# Provisioning Services (biotic & Abiotic)
## Others Abiotic

```{r ES_Provision_Abiotic}
#CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 12)

CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 15)

```

# CICES

1. .large.bg-yellow[Provisioning Services (biotic & Abiotic)]
1. .large.bg-yellow[Regulation & Maintenance (biotic & Abiotic)]
1. .large.bg-yellow[Cultural]

# Regulation & Maintenance (biotic & Abiotic)

## Biochemical or physical inputs to ecosystems

.pull-left[
**Territorial Question**

*Is*	]

.pull-right[
**Industrial Question**

*The *
]

```{r}
#CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 12)

CICES_filter(ID=c("2.1.1.1", "2.1.1.2", "2.1.2.1", "2.1.2.2", "2.1.2.3"), size = 15)

```

# Regulation & Maintenance (biotic & Abiotic)
## Regulation of physical, chemical, biological conditions

.pull-left[
**Territorial Question**

*Is*	]

.pull-right[
**Industrial Question**

*The *
]

```{r}
#CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 12)

CICES_filter(ID=c("2.2.1.1", "2.2.1.2", "2.2.1.3", "2.2.1.4", "2.2.1.5" ), size = 15)

```

# Regulation & Maintenance (biotic & Abiotic)
## Regulation of physical, chemical, biological conditions

.pull-left[
**Territorial Question**

*Is*	]

.pull-right[
**Industrial Question**

*The *
]

```{r}
#CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 12)

CICES_filter(ID=c("2.2.2.1", "2.2.2.2", "2.2.2.3", "2.2.3.1", "2.2.3.2", "2.2.4.1", "2.2.4.2", "2.2.5.1", "2.2.5.2", "2.2.6.1", "2.2.6.2" ), size = 15)

```

# Regulation & Maintenance (biotic & Abiotic)
## Regulation of physical, chemical, biological conditions

.pull-left[
**Territorial Question**

*Is*	]

.pull-right[
**Industrial Question**

*The *
]

```{r}
#CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 12)

CICES_filter(ID=c("2.2.4.1", "2.2.4.2", "2.2.5.1", "2.2.5.2", "2.2.6.1", "2.2.6.2" ), size = 15)
```

# CICES

1. .large.bg-yellow[Provisioning Services (biotic & Abiotic)]
1. .large.bg-yellow[Regulation & Maintenance (biotic & Abiotic)]
1. .large.blue[Cultural]

# Cultural (Biotic) 
## Direct contact with Nature

.pull-left[
**Territorial Question**

*Is*	]

.pull-right[
**Industrial Question**

*The *
]

```{r}
CICES_filter(ID=c("3.1.1.1", "3.1.1.2", "3.1.2.1", "3.1.2.2", "3.1.2.3", "3.1.2.4"), size = 15)
```

# Cultural (Biotic) 
## Indirect contact with Nature

.pull-left[
**Territorial Question**

*Is*	]

.pull-right[
**Industrial Question**

*The *
]

```{r}
CICES_filter(ID=c("3.2.1.1","3.2.1.2","3.2.1.3","3.2.2.1","3.2.2.2"), size = 15)

```

# Cultural (Abiotic) 
## Direct and Indirect link with Nature

.pull-left[
**Territorial Question**

*Is*	]

.pull-right[
**Industrial Question**

*The *
]

```{r}
CICES_filter(ID=c("6.1.1.1","6.1.2.1","6.2.1.1","6.2.2.1"), size = 15)
```

---
class: middle, center

# Thanks !
